### 2020-01-23 ChapterImplementation/chapterImplementation.tex
Updated: Lots of TODOs added to Implementation
Updated: Server-region topolgy diagrams and description

\chapter{Implementation}
In this section will discuss our implementation of AP, The following will be looked at in detail: \begin{itemize}
	\item An overview of the system architecture: How the servers are deployed in the cloud and how they communicate with a client, along with potential deployments to be investigated in the future.
	\item A breakdown of the components of each server.
	\item The algorithms used by the servers to implement AP.
	\item The life cycle of a simulated object as a finite state machine (FSM).
	\item The features and implementation details of the visualiser, including a breakdown of the components of a client and future work to be carried out on the visualiser.
\end{itemize}

@@

\section{System Architecture}
%TODO: Mention we're using AWS EC2 G2 instances
The simulation space is partitioned into regions, with each region consisting of its own instance of PhysX running on a dedicated GPU-enabled machine in the cloud. The boundary between regions is defined as a vertical plane, two-dimensionally dividing the simulation space into one region per server. The network library RakNet is used for all message passing between servers. RakNet ensures messages exhibit best effort and are received in sent order.

@@

\subsection{Server-Region Topology}
Server-region topologies and how they affect the communication requirements between servers will now be discussed. 
AP allows for the simulation space to be partitioned into any topology. In terms of communication, all servers need to communicate with all of their neighbours in order to satisfy the solution to the corner case, as described in \ref{CornerCase}. We define a neighbour as any server that shares a region boundary, including at a corner. The simplest topology that can be used is a column layout, as shown in \ref{ServerColumnLayout}. In column layout, servers have at most two neighbours, this topology therefore has the fewest server connection requirements.

\definecolor{rvwvcq}{rgb}{0.08235294117647059,0.396078431372549,0.7529411764705882}
\definecolor{sim}{rgb}{0,0.2,0.5}
\begin{figure}[!t]	\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm,scale=1.5]
	\clip(-2.25,0) rectangle (8.4,3.75);
	\fill[line width=0.8pt,color=sim,fill=sim,fill opacity=0.1] (-2.25,3) -- (-2.25,0) -- (8.25,0) -- (8.25,3) -- cycle;
	\draw (-1.5,3.5) node[anchor=center] {Server 0};
	\draw (1.5,3.5) node[anchor=center] {Server 1};
	\draw (4.5,3.5) node[anchor=center] {\textbf{...}};
	\draw (7.5,3.5) node[anchor=center] {Server N-1};
	\draw [line width=2pt] (0,0)-- (0,3);
	\draw [line width=2pt] (3,0)-- (3,3);
	\draw [line width=2pt] (6,0)-- (6,3);
	\end{tikzpicture}
	\centering
	\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm]
	\clip(-4,0) rectangle (7,1.5);
	\draw [line width=2pt] (-0.5,0.7)-- (-0.3,0.7);
	\draw (-0.1,0.7) node[anchor=west] {Server-Region Boundary};
	\end{tikzpicture}
	\caption{Column Layout}
	\label{ServerColumnLayout}
\end{figure}

\begin{figure}[!t]
	\begin{subfigure}{.5\textwidth}
		\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm,scale=1.2]
		\fill[line width=0.8pt,color=sim,fill=sim,fill opacity=0.1] (-3,3) -- (-3,-2) -- (3,-2) -- (3,3) -- cycle;
		\draw [line width=2pt] (-3,0)-- (3,0);
		\draw [line width=2pt] (0,3)-- (0,0);
		\draw (-1.5,2.5) node[anchor=center] {Server 0};
		\draw (1.5,2.5) node[anchor=center] {Server 1};
		\draw (0,-1) node[anchor=center] {Server 2};
		\end{tikzpicture}
		\centering
		\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm]
		\draw [line width=2pt] (-2.5,0.5)-- (-2.3,0.5);
		\draw (-2.1,0.5) node[anchor=west] {Region Boundary};
		\end{tikzpicture}
		\caption{3 Server Corner Layout}
		\label{3ServerCornerLayout}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm,scale=1.2]
		%	\clip(-3,-3) rectangle (3,3);
		\fill[line width=0.8pt,color=sim,fill=sim,fill opacity=0.1] (-3,3) -- (-3,-3) -- (3,-3) -- (3,3) -- cycle;
		\draw [line width=2pt] (-3,0)-- (3,0);
		\draw [line width=2pt] (0,3)-- (0,0);
		\draw (-1.5,2.5) node[anchor=center] {Server 0};
		\draw (1.5,2.5) node[anchor=center] {Server 1};
		\draw (-1.5,-2.5) node[anchor=center] {Server 2};
		\draw (1.5,-2.5) node[anchor=center] {Server 3};
		\draw [line width=2pt] (0,0)-- (0,-3);
		\end{tikzpicture}
		\centering
		\caption{4 Server Corner Layout}
		\label{4ServerCornerLayout}
	\end{subfigure}
	\caption{Corner Layouts}
	\label{ServerCornerLayout}
\end{figure}

\subsection{Individual Server Breakdown}

@@

@@

>>>>

\chapter{Implementation}
In this section will discuss our implementation of AP, The following will be looked at in detail: \begin{itemize}
	\item An overview of the system architecture: How the servers are deployed in the cloud and how they communicate with a client, along with potential deployments to be investigated in the future.
	%TODO: Add aura implmentation?
	\item A breakdown of the components of each server.
	\item The algorithms used by the servers to implement AP.
	\item The life cycle of a simulated object as a finite state machine (FSM).
	\item The features and implementation details of the visualiser, including a breakdown of the components of a client and future work to be carried out on the visualiser.
\end{itemize}

@@

\section{System Architecture}
%TODO: Mention we're using AWS EC2 G2 instances
%TODO: Mention Gtest for automated tests and experiments
The simulation space is partitioned into regions, with each region consisting of its own instance of PhysX running on a dedicated GPU-enabled machine in the cloud. The boundary between regions is defined as a vertical plane, two-dimensionally dividing the simulation space into one region per server. The network library RakNet is used for all message passing between servers. RakNet ensures messages exhibit best effort and are received in sent order.

@@

%TODO: Mention how auras are implemented: Aura is a trigger volume around objects. Boundary has a trigger volume, illustrate with diagram. Justify this. Mention corner case, aura is sent to both servers, illustrate with diagram. Is this mentioned elsewhere?

\subsection{Server-Region Topology}
Server-region topologies and how they affect the communication requirements between servers will now be discussed. 
AP allows for the simulation space to be partitioned into any topology. In terms of communication, all servers need to communicate with all of their neighbours in order to satisfy the solution to the corner case, as described in \ref{CornerCase}. We define a neighbour as any server that shares a region boundary, including at a corner.

The simplest topology that can be used is a column layout, as shown in Fig. \ref{ServerColumnLayout}. In column layout, servers have at most 2 neighbours, this topology therefore has the fewest server connection requirements. It should be noted however, that fewer server connection requirements doesn't necessarily mean less network traffic as the traffic between 2 servers is dependent on the activity of the simulation near the server boundary.

\definecolor{rvwvcq}{rgb}{0.08235294117647059,0.396078431372549,0.7529411764705882}
\definecolor{sim}{rgb}{0,0.2,0.5}

\begin{figure}[!t]	
	\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm,scale=1.5]
	\clip(-2.25,0) rectangle (8.4,3.75);
	\fill[line width=0.8pt,color=sim,fill=sim,fill opacity=0.1] (-2.25,3) -- (-2.25,0) -- (8.25,0) -- (8.25,3) -- cycle;
	\draw (-1.5,3.5) node[anchor=center] {Server 0};
	\draw (1.5,3.5) node[anchor=center] {Server 1};
	\draw (4.5,3.5) node[anchor=center] {\textbf{...}};
	\draw (7.5,3.5) node[anchor=center] {Server N-1};
	\draw [line width=2pt] (0,0)-- (0,3);
	\draw [line width=2pt] (3,0)-- (3,3);
	\draw [line width=2pt] (6,0)-- (6,3);
	\end{tikzpicture}
	\centering
	\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm]
	\clip(-4,0) rectangle (7,1.5);
	\draw [line width=2pt] (-0.5,0.7)-- (-0.3,0.7);
	\draw (-0.1,0.7) node[anchor=west] {Server-Region Boundary};
	\end{tikzpicture}
	\caption{Column Layout}
	\label{ServerColumnLayout}
\end{figure}

Any topology more complex than columns will result in corners being present in the topology. The simplest corner that can exist is between three servers, as shown in Fig. \ref{3ServerCornerLayout}. All three server must communicate when a corner between three servers exists, this is required for the solution to the corner case (as described in \ref{CornerCase}). For example, in  Fig. \ref{3ServerCornerLayout}, a cluster of objects being hosted by server 2 may exist across the boundary between server 0, objects on the edge of the cluster may be positioned deep into server 0's region. In addition a cluster of objects being hosted on server 1 may exist across the boundary between server 1 and server 0 with some objects in the cluster being deep into server 0's region. Without the auras from the server 0 - server 1 boundary being sent to server 2 and vice versa, the two clusters will be unaware of each other's existence. From Server 0's perspective, the two clusters may have overlapping auras, and so should be being simulated on the same server. In order to prevent this, the auras from the boundaries of all neighbours need to be exchanged.

\begin{figure}[!t]
	\begin{subfigure}{.5\textwidth}
		\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm,scale=1.2]
		\fill[line width=0.8pt,color=sim,fill=sim,fill opacity=0.1] (-3,3) -- (-3,-2) -- (3,-2) -- (3,3) -- cycle;
		\draw [line width=2pt] (-3,0)-- (3,0);
		\draw [line width=2pt] (0,3)-- (0,0);
		\draw (-1.5,2.5) node[anchor=center] {Server 0};
		\draw (1.5,2.5) node[anchor=center] {Server 1};
		\draw (0,-1) node[anchor=center] {Server 2};
		\end{tikzpicture}
		\centering
		\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm]
		\draw [line width=2pt] (-2.5,0.5)-- (-2.3,0.5);
		\draw (-2.1,0.5) node[anchor=west] {Region Boundary};
		\end{tikzpicture}
		\caption{3 Server Corner Topology}
		\label{3ServerCornerLayout}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm,scale=1.2]
		%	\clip(-3,-3) rectangle (3,3);
		\fill[line width=0.8pt,color=sim,fill=sim,fill opacity=0.1] (-3,3) -- (-3,-3) -- (3,-3) -- (3,3) -- cycle;
		\draw [line width=2pt] (-3,0)-- (3,0);
		\draw [line width=2pt] (0,3)-- (0,0);
		\draw (-1.5,2.5) node[anchor=center] {Server 0};
		\draw (1.5,2.5) node[anchor=center] {Server 1};
		\draw (-1.5,-2.5) node[anchor=center] {Server 2};
		\draw (1.5,-2.5) node[anchor=center] {Server 3};
		\draw [line width=2pt] (0,0)-- (0,-3);
		\end{tikzpicture}
		\centering
		\caption{4 Server Corner Topology}
		\label{4ServerCornerLayout}
	\end{subfigure}
	\caption{Corner Layouts}
	\label{ServerCornerLayout}
\end{figure}

An example of a topology that includes corners with no more than 3 servers neighbouring is illustrated in Fig. \ref{BrickLayout}. In this topology, the maximum number of server connections required would be 6, as server 3 has 6 neighbouring servers. It should be noted that not all servers need to communicate with each other, for example server 0 does not neighbour with servers 4 or 6, so no communication is needed.

\begin{figure}[!t]	
	\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm,scale=0.875]
		\fill[line width=0.8pt,color=sim,fill=sim,fill opacity=0.1] (-6,-9) -- (-6,0) -- (12,0) -- (12,-9) -- cycle;
		\draw [line width=2pt] (-3,-3)-- (3,-3);
		\draw [line width=2pt] (-3,-3)-- (-3,0);
		\draw [line width=2pt] (-3,0)-- (3,0);
		\draw [line width=2pt] (3,0)-- (3,-3);
		\draw [line width=2pt] (-6,-6)-- (0,-6);
		\draw [line width=2pt] (-6,-6)-- (-6,-3);
		\draw [line width=2pt] (-6,-3)-- (0,-3);
		\draw [line width=2pt] (0,-3)-- (0,-6);
		\draw [line width=2pt] (0,-6)-- (6,-6);
		\draw [line width=2pt] (0,-6)-- (0,-3);
		\draw [line width=2pt] (0,-3)-- (6,-3);
		\draw [line width=2pt] (6,-3)-- (6,-6);
		\draw [line width=2pt] (3,-3)-- (9,-3);
		\draw [line width=2pt] (3,-3)-- (3,0);
		\draw [line width=2pt] (3,0)-- (9,0);
		\draw [line width=2pt] (9,0)-- (9,-3);
		\draw [line width=2pt] (6,-6)-- (12,-6);
		\draw [line width=2pt] (6,-6)-- (6,-3);
		\draw [line width=2pt] (6,-3)-- (12,-3);
		\draw [line width=2pt] (12,-3)-- (12,-6);
		\draw [line width=2pt] (-3,-9)-- (3,-9);
		\draw [line width=2pt] (-3,-9)-- (-3,-6);
		\draw [line width=2pt] (-3,-6)-- (3,-6);
		\draw [line width=2pt] (3,-6)-- (3,-9);
		\draw [line width=2pt] (3,-9)-- (9,-9);
		\draw [line width=2pt] (3,-9)-- (3,-6);
		\draw [line width=2pt] (3,-6)-- (9,-6);
		\draw [line width=2pt] (9,-6)-- (9,-9);
		\draw (0.0,-1.5) node[anchor=center] {Server 0};
		\draw (6,-1.5) node[anchor=center] {Server 1};
		\draw (-3,-4.5) node[anchor=center] {Server 2};
		\draw (3,-4.5) node[anchor=center] {Server 3};
		\draw (9,-4.5) node[anchor=center] {Server 4};
		\draw (0,-7.5) node[anchor=center] {Server 5};
		\draw (6,-7.5) node[anchor=center] {Server 6};
	\end{tikzpicture}
	\centering
	\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm]
	\clip(-4,0) rectangle (7,1.5);
	\draw [line width=2pt] (-0.5,0.7)-- (-0.3,0.7);
	\draw (-0.1,0.7) node[anchor=west] {Server-Region Boundary};
	\end{tikzpicture}
	\caption{An example topology using only 3-server corners}
	\label{BrickLayout}
\end{figure}

An example of a topology that uses 4-server corners is illustrated in Fig. \ref{GridLayout}. In this topology the maximum number of server connections required would be 8, as server 4 has 8 neighbouring nodes. It should be noted that not all servers need to communicate with each other, for example server 0 does not need to communicate with servers 2 or 5 as they are not neighbouring servers.

\begin{figure}[!t]
	\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm]
	\fill[line width=0.8pt,color=sim,fill=sim,fill opacity=0.1] (-3,3) -- (-3,-6) -- (6,-6) -- (6,3) -- cycle;
	\draw [line width=2pt] (-3,0)-- (6,0);
	\draw [line width=2pt] (0,3)-- (0,-6);
	\draw [line width=2pt] (-3,-3)-- (6,-3);
	\draw [line width=2pt] (3,3)-- (3,-6);
	\draw (-1.5,1.5) node[anchor=center] {Server 0};
	\draw (1.5,1.5) node[anchor=center] {Server 1};
	\draw (4.5,1.5) node[anchor=center] {Server 2};
	\draw (-1.5,-1.5) node[anchor=center] {Server 3};
	\draw (1.5,-1.5) node[anchor=center] {Server 4};
	\draw (4.5,-1.5) node[anchor=center] {Server 5};
	\draw (-1.5,-4.5) node[anchor=center] {Server 6};
	\draw (1.5,-4.5) node[anchor=center] {Server 7};
	\draw (4.5,-4.5) node[anchor=center] {Server 8};
	\end{tikzpicture}
	\centering
	\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm]
	\clip(-4,0) rectangle (7,1.5);
	\draw [line width=2pt] (-0.5,0.7)-- (-0.3,0.7);
	\draw (-0.1,0.7) node[anchor=west] {Server-Region Boundary};
	\end{tikzpicture}
	\caption{An example topology using 4-server corners}
	\label{GridLayout}
\end{figure}

%TODO: Talk about adaptive server boundaries in the future. Talk about assumptions that clusters do not cross width between nodes and how adaptive boundaries could lead to this

\subsection{Individual Server Breakdown}
%TODO: Describe diagram

@@

%TODO: Add client-created server regions feature

@@

%TODO: Client breakdown + diagram
